%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\definecolor{color1}{rgb}{0.22,0.45,0.70}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Fábio F.}{O. Silva}
%\title{CV}                               % optional, remove / comment the line if not wanted
%\address{my address, line 1, line 2, line 3, postcode}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+55~(83)~9~8858~2685}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{fabio.fernando.osilva@gmail.com}                               % optional, remove / comment the line if not wanted
%\homepage{ffosilva.github.io}                         % optional, remove / comment the line if not wanted
\social[github]{ffosilva}                         % optional, remove / comment the line if not wanted
\social[linkedin]{ffosilva}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

%\small{Computer Science student completing the final year of a bachelor's degree. Passionate about Cyber Security, DevOps, Cloud Computing, music and travelling.}

\section{Experience}

\vspace{6pt}

\begin{itemize}

\item{\cventry{Feb 2025 -- Present}{Senior Software Engineer, Full Time}{QuintoAndar}{São Paulo, Brazil (Remote)}{}{\vspace{3pt}Designing and implementing AI-powered multi-agentic solutions to enhance and scale inside sales operations. Driving efficiency and customer engagement using Large Language Models (LLMs) on AWS.\\
{\color{gray} Tech Stack:} AWS, Python, LLMs, AI Agents.}}

\vspace{6pt}

\item{\cventry{Oct 2020 -- Jan 2025}{Senior Software Engineer, Full Time}{VTEX}{João Pessoa, Brazil}{}{\vspace{3pt}Part of the Payments team, responsible for maintaining a high-throughput, PCI-compliant Payment Gateway and related financial products. Executed stack modernization and infrastructure efficiency initiatives, reducing costs while improving system reliability and resiliency.\\
{\color{gray} Tech Stack:} AWS, .NET, C\#, SQL, Redis, ActiveMQ.}}

\vspace{6pt}

\item{\cventry{Apr 2020 -- Sep 2020}{Software Engineer, Full Time}{Scontain U.G.}{Dresden, Germany}{}{\vspace{3pt}Contributed to the core SCONE confidential computing runtime and co-developed a modified Intel SGX Linux kernel driver to support selective enclave eviction. Led the design and implementation of a Kubernetes device plugin/driver to enable SGX usage in containerized pods.\\
{\color{gray} Tech Stack:} C, Docker, Bash, Intel SGX, Python, Gitlab, CI/CD, Linux.}}

\vspace{6pt}

\item{\cventry{Jan 2017 -- Mar 2020}{Research Assistant \& Software Developer}{Distributed Systems Laboratory}{Campina Grande, Brazil}{}{\vspace{3pt}Developed a secure cloud execution ecosystem leveraging Intel SGX hardware-enforced security extensions. Built mechanisms to protect workloads against attacks from privileged system users (cloud operators/sysadmins) and compromised software layers (hypervisors).\\
		{\color{gray} Tech Stack:} Docker, SCONE, OpenStack, Intel SGX, C++, MongoDB, Python, Apache Kafka, Git.}}

\vspace{6pt}

\item{\cventry{Dec 2017 -- Jan 2018}{Research Assistant \& Software Developer, Intern}{Technische Universität Dresden}{Dresden, Germany}{}{\vspace{3pt}Improved Python runtime support and performance within SCONE confidential enclaves. Modified CPython source code (C) and integrated the Intel Math Kernel Library (MKL) to run securely inside SGX environments.\\
		{\color{gray} Tech Stack:} Docker, SCONE, Intel SGX, C, Python, musl libc, PySpeed, PyPy, Git.}}

\vspace{6pt}

\item{\cventry{Jan 2016 -- Dec 2016}{Software Developer}{PrivIoT}{Campina Grande, Brazil}{}{\vspace{3pt}Researched privacy-by-design patterns for Internet of Things (IoT) architectures. Developed and validated reference IoT applications as case studies to verify secure software development guidelines.\\
{\color{gray} Tech Stack:} MongoDB, Python, Flask, Ionic, JavaScript, AngularJS, D3.js, Git.}}

\newpage
%\vspace{6pt}

\item{\cventry{Aug 2014 -- Dec 2015}{Data Analyst \& Software Developer}{Analytics Lab}{Campina Grande, Brazil}{}{\vspace{3pt}Analyzed 3 years of agricultural cohort data from 200+ farmers, creating interactive data visualizations with JavaScript. Developed a GPS-enabled mobile application for the public transportation sector to map bus stops, validate routes, and enrich municipal datasets.\\
{\color{gray} Tech Stack:} R, D3.js, Chart.js, Android SDK, Git.}}

\vspace{6pt}

\item{\cventry{Nov 2012 -- Jul 2014}{Software Developer \& Research Assistant}{Software Practices Laboratory}{Campina Grande, Brazil}{}{\vspace{3pt}Developed an Eclipse plug-in that automates the migration and optimization of Java Collections Framework (JCF) classes in source code. (Demo: \url{https://www.youtube.com/watch?v=PUIEPlVmI-Q})\\
		{\color{gray} Tech Stack:} Java, Eclipse, Eclipse JDT, Design Patterns, Git.}}

% \newpage
\vspace{6pt}

\item{\cventry{Nov 2011 -- Feb 2012}{Web \& Android Developer, Intern}{9Ideia Digital}{Campina Grande, Brazil}{}{\vspace{3pt}Developed web applications and custom Content Management Systems (CMS) using the LAMP stack (Linux, Apache, MySQL, PHP). Engineered Android applications utilizing the Android SDK as part of a technical internship.\\
		{\color{gray} Tech Stack:} Apache, HTML, CSS, JavaScript, Java, Android SDK, jQuery, PHP, MySQL, Git.}}

\end{itemize}

\section{Voluntary Experience}

\vspace{6pt}

\begin{itemize}
	
\item{\cventry{Nov 2015 -- Oct 2016}{Device Tree Maintainer}{CyanogenMod Project}{}{}{\vspace{3pt}Added initial support to Sony Xperia Z3 Dual (D6633) on CyanogenMod project. It is also the device tree maintainer's role to perform code reviews of contributions made through commits on Gerrit Code Review system. \\
		{\color{gray} Tech Stack:} Linux Kernel, Android Build Engine, AOSP, Android Architecture, C++, Makefile, Gerrit, Git.}}

\end{itemize}

\section{Education}

\vspace{5pt}

\begin{itemize}

\item{\cventry{2021}{C++ Nanodegree}{Udacity, Inc.}{Remote}{}{}}

\item{\cventry{2018 -- 2020}{M.Sc. Computer Science, Information Security}{Federal University of Campina Grande}{Campina Grande, Brazil}{}{}}

\item{\cventry{2012 -- 2017}{B.Sc. Computer Science}{Federal University of Campina Grande}{Campina Grande, Brazil}{}{}}

\item{\cventry{2010 -- 2012}{Certificate in Information Technology}{Infogenius Technical College}{Campina Grande, Brazil}{}{}}

\end{itemize}

\newpage
\section{Notable Projects}

\vspace{5pt}

\begin{itemize}

\item{\cventry{}{Lead Developer}{Kafka Proxy SGX}{}{Software}{\vspace{3pt}A transparent, drop-in security proxy that encrypts in-transit and at-rest Kafka cluster data. Leverages confidential computing (Intel SGX) to protect sensitive data and encryption keys from infrastructure operators and host-level threats.}}
	
\vspace{6pt}

\item{\cventry{}{Founder \& Developer}{RunMusic App}{}{Android Application}{\vspace{3pt}An Android application that synchronizes music playback tempo with the runner's real-time pace. Awarded 1st place in the Entrepreneurship category of the III Campus Mobile national contest.}}

\vspace{6pt}
%\newpage

\item{\cventry{}{Academic Project}{Java Compiler}{}{Compiler Course}{\vspace{3pt}Developed a Java-like compiler using JFlex (lexical analyzer) and CUP (LALR parser). The front-end parses standard Java syntax features, while the back-end compiles to target Assembly code.}}

\end{itemize}

\section{Key Skills}

\vspace{6pt}

\begin{itemize}

\item \textbf{Programming Languages:} Python, C\# (.NET), C/C++, Java, JavaScript, SQL, R.

\vspace{6pt}

\item \textbf{Cloud \& Infrastructure:} AWS, Docker, Kubernetes, OpenStack, Linux, Git, CI/CD.

\vspace{6pt}

\item \textbf{Databases \& Middleware:} SQL, MongoDB, Redis, ActiveMQ, Apache Kafka.

\end{itemize}

\section{Languages}

\vspace{6pt}

\begin{itemize}

\item{Portuguese \textit{(native)}}
\item{English \textit{(professional proficiency)}}

\end{itemize}

\section{Awards}

\vspace{6pt}
 
\begin{itemize}

\item{\textbf{2015:} Best application in Entrepreneurship Category of III Campus Mobile national contest, promoted by Instituto Embratel-Claro.}

\item{\textbf{2011:} 1st place on programming contest promoted by Infogenius Technical College.}

\end{itemize}

\newpage
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{abbrv}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
